%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Glossier} % Organization
    {Remote/New York} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented features for Glossier POS such as cash scaling support for Retail stores, localization to support London store, and migrated the Stripe-mandated SDK upgrade.}
        \item {Contributed to the successful re-platform of Glossier e-commerce and retail store, resulting in streamlined operations. }
        \item {Led the development and implementation of product set strategy for retail stores, resulting in improved customer experience.}
        \item {Developed a script to semi-automate the creation of products sets on Shopify, significantly increasing efficiency by more than 70\%.}
        \item {Collaborated with cross-functional teams, including retail, data, and accounting, to ensure a smooth transition to Shopify.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Medtronic} % Organization
    {Northridge, California} % Location
    {Dec. 2020 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead iOS development for adding support to new Continuous Glucose Monitor device to existing insulin pumps.}
        \item {Assume full ownership of features in all phases of design, implementation, unit and integration testing, documentation, deployment, and production troubleshooting.}
        \item {Contributed to system requirement software, user interface design document and software configuration management plans for Class II mobile apps.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Software Engineer} % Job title
    {Medtronic} % Organization
    {Northridge, California} % Location
    {Oct. 2018 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed native iOS applications communicating with BLE insulin pump and cloud platform services.}
        \item {Designed and implemented secure transfer of secured keys from server.}
        \item {Developed help guide functionality which features offline capability, multiple language support and auto-updates.}
        \item {Worked with pump software team to resolve Bluetooth communication issues present in iPhones.}
        \item {Defined and performed feature design documentation and requirement definitions in compliance with FDA for Class II and Class III mobile apps.}
        \item {Implemented business requirements, working with cross-functional stakeholders to define use case and feature scope for mobile app.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer/Mobile Developer} % Job title
    {ISBX} % Organization
    {Los Angeles, California} % Location
    {May. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical lead of 3-5 mobile engineers for iOS projects.}
        \item {Designed mobile architecture and developed features for native Android and iOS applications.}
        % \item {Maintained industry coding standards and best practices through code reviews and providing mentorship to other developers.}
        \item {Worked with clients in a tight feedback loop to validate product requirements.}
        \item {Collaborated closely UI/UX designers and project managers to deliver projects on-time and with the highest standard.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {ISBX} % Organization
    {Los Angeles, California} % Location
    {Feb. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Angular a document and file storage management web application. Use of third party seIntegrate Stripe's payment APIs to process payment transactions.}
        \item {Responsible for increasing code coverage for existing web applications. }
        \item {Collaboratively work with offshore teams to maintain project timelines and expectations.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
